---
title: "ML Email spam"
author: "Bochen Wang"
date: "5/16/2018"
output: html_document
---

```{r}
setwd("~/Downloads/spam_data")
train = read.csv('train.csv',header = FALSE)
summary(train)
trainLabel = read.csv('trainLabel.csv', colClasses='factor', numerals = "no.loss", header = FALSE)
summary(trainLabel)
```

```{r}
library(e1071)
svm = svm(train,trainLabel, type = 'C-classification')
summary(svm)
typeof(trainLabel)
summary(trainLabel)
```

```{r}
setwd("~/Downloads/spam_data")
test = read.csv('test.csv',header = FALSE)
testLabel = read.csv('testLabel.csv',colClasses='factor', numerals = "no.loss",header = FALSE)
```

```{r}

y_pred = predict(svm,train)
y_pred
out = table(y_pred,t(trainLabel))
out
chisq.test(out)
summary(trainLabel)
```
```{r}
library(lattice)
library(ggplot2)
library(caret)
confusionMatrix(out)
```

```{r}
y_test = predict(svm,test)
y_test
out1 = table(y_test,t(testLabel))
out1
chisq.test(out1)
```

```{r}
confusionMatrix(out1)
```
```{r}
confusionMatrix(out)
```


library(naivebayes)
trainLabel
bayes = naiveBayes(train,trainLabel, type = 'C-classification')
y_pred = predict(bayes,train, type = 'raw')
out2 = table(y_pred, t(trainLabel))
length(y_pred)
length(t(trainLabel))
out2
chisq.test(out2)

svm = svm(train,trainLabel, type = 'C-classification')
summary(svm)
typeof(trainLabel)
summary(trainLabel)

y_test = predict(svm,test)
out1 = table(y_test,t(testLabel))
out1
chisq.test(out1)

yf = factor(y)
model5 = svm(x,yf)
summary(model5)
y_pred = predict(model5,x)
out = table(y_pred,yf)
out
chisq.test(out)